systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-18 paper/trunk/systemfit_summary.tex
made small comment to test the repos on the new server
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@587 591db2bd-e0a0-4d22-8c19-2192dbb7da31
made another small comment to test the repos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@588 591db2bd-e0a0-4d22-8c19-2192dbb7da31
really small change after read. it's ready for submission!
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@589 591db2bd-e0a0-4d22-8c19-2192dbb7da31
changed a few line breaks that each sentence starts in a new line now
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@

The \pkg{systemfit} package was originally developed to fit
simultaneous equations for forestry datasets. Forestry datasets
typically contain observations of many inexpensive observations (stem
diameter) and few expensive observations such as stem height and being
able the utilize as many observations as possible is advantageous. As
most software packages simply drop data points that do not contain
both observations, the \pkg{systemfit} package currently does not
allow for unbalanced datasets, but it is our intention to include this
capability for certain estimation methods in future releases.

In this article, we have described some of the basic features of the
\pkg{systemfit} package for estimation of linear systems of
equations. It has been tested on a variety of datasets and has
produced satisfactory for a few years. While more sophisticated tools
exist, the \pkg{systemfit} package will perform the basic fitting
methods. We wish to include more sophisticated estimation methods such
as full-information maximum likelihood and generalized methods of
moments.

>>>>

In this article, we have described some of the basic features of the
\pkg{systemfit} package for estimation of linear systems of
equations with various estimation methods.
Many details of the estimation can be controlled by the user.
Furthermore, the package provides some statistical tests
for parameter restrictions and consistency of 3SLS estimation.
It has been tested on a variety of datasets and has produced satisfactory
for a few years.%
\footnote{
The code to replicate results published in the literature is given
in the documentation of the cooresponding data sets
included in the \pkg{systemfit} package
(see the documentation of \code{GrunfeldGreen}, \code{GrunfeldTheil},
\code{KleinI} and \code{kmenta}).
}
While the \pkg{systemfit} package performs the basic fitting methods,
more sophisticated tools exist.
We hope to implement missing functionalities
in the near future.
Some of these are discussed in the following.

\paragraph{Unbalanced datasets}
Currently, the \pkg{systemfit} package requires
that all equations have the same number of observations.
However, many data sets have unbalanced observations.%
\footnote{
For instance,
forestry datasets typically contain observations of many inexpensive
observations (stem diameter) and few expensive observations such
as stem height.
}
Simply dropping data points
that do not contain observations for all equations
may considerably reduce the number of observations,
and thus, the information utilized in the estimation.
Hence, it is our intention to include the capability for estimations
with unbalanced data sets as described in \citet{schmidt77}
in future releases of \pkg{systemfit}.

\paragraph{Serial correlation and heteroscedasticity}
For all of the methods developed in the package, the disturbances of
the individual equations are assumed to be independent and identically
distributed (iid).
The package could be enhanced by the inclusion of methods to fit
equations with serially correlated and heteroscedastic disturbances.

\paragraph{Estimation methods}
We wish to include more sophisticated estimation methods such
as limited-information maximum likelihood (LIML),
full-information maximum likelihood (FIML),
and generalized methods of moments (GMM), in future releases.

%% testing for the new svn repos
%% It works great!!!
